Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-03 documentation/paper.tex
Rearranged semi-supervised learning section

@@

\begin{enumerate}
    \item Train $NN(x)$ for a single epoch on the combined set $\varsigma \cup \upsilon$, using the predefined ground truths for $\varsigma$ (with a mean squared error loss function) and the most recently calculated gravitational gradients for $\upsilon$.
    \item Calculate predictions $p$ with $NN(x)$ on the entirety of $\upsilon$. Calculate $GravDiff(p, \psi, g)$ and record the resulting gradients for the next iteration.
    \item Increment $g$ by $\delta_g$. At the beginning, when $g = 0$, training will be entirely based on the labeled set $\varsigma$, and progressively, over the course of a run, the gravitational effect increases with $g$.
\end{enumerate}

@@

To arrive at an effective discriminator, the network first trains on a smaller amount of imperfect data. Because the ground truth data is imperfect, training on a relatively small set for a short period of time (potentially using regularization, in addition) ensures that the network will be less likely to overfit and its learned function will be simpler. This is in line with the objective, since, assuming the training inputs are normalized correctly, it should be simpler to discriminate between classes of particles than calibration runs.

The essence of this algorithm, then, is a positive feedback loop in which, by including the network's most confident predictions in the training set, the simpler function that is desired is reinforced, even when the original ground truths teach the more complex function that would likely have been arrived at by a conventional supervised learning system.

>>>>

Semi-supervised learning is the idea of training a machine learning model on a set of labeled data in addition to a set of unlabeled data. This has the advantage of requiring fewer labels to be collected than conventional supervised learning. However, it also has a very powerful advantage when training data is impure and the function to be learned is relatively simple (not simple in that it can be easily calculated by a person, but simple in that it does not require a huge set of training data). It allows a neural network to reinforce its own decisions.

In both of the semi-supervised learning algorithms applied, to arrive at an effective discriminator, the network first trains on a smaller amount of imperfect data. Because the ground truth data is imperfect, training on a relatively small set for a short period of time (potentially using regularization, in addition) ensures that the network will be less likely to overfit and its learned function will be simpler. This is in line with the objective, since, assuming the training inputs are normalized correctly, it should be simpler to discriminate between classes of particles than calibration runs.

The essence of this algorithm, then, is a positive feedback loop in which, by using the network's most confident predictions in the training process, the desired (simpler) function is reinforced, when a conventional supervised learning system would have learned the more complex function that is taught by the ground truths.

@@

\begin{enumerate}
    \item Train $NN(x)$ for a single epoch on the combined set $\varsigma \cup \upsilon$, using the predefined ground truths for $\varsigma$ (with a mean squared error loss function) and the most recently calculated gravitational gradients for $\upsilon$.
    \item Calculate predictions $p$ with $NN(x)$ on the entirety of $\upsilon$. Calculate $GravDiff(p, \psi, g)$ and record the resulting gradients for the next iteration.
    \item Increment $g$ by $\delta_{g}$. At the beginning, when $g = 0$, training will be entirely based on the labeled set $\varsigma$, and progressively, over the course of a run, the gravitational effect increases with $g$.
\end{enumerate}

@@
